Regression Models Week 1
========================

#Question 1
Consider the data set given below
```{r}
x <- c(0.18, -1.54, 0.42, 0.95)
```
And weights given by
```{r}
w <- c(2, 1, 3, 1)
```
Give the value of μ that minimizes the least squares equation

```{r}
x_rep <- rep(x, w)
mean(x_rep)
```
#Question 2
Consider the following data set
```{r}
x <- c(0.8, 0.47, 0.51, 0.73, 0.36, 0.58, 0.57, 0.85, 0.44, 0.42)
y <- c(1.39, 0.72, 1.55, 0.48, 1.19, -1.59, 1.23, -0.65, 1.49, 0.05)
```
Fit the regression through the origin and get the slope treating y as the outcome and x as the regressor. (Hint, do not center the data since we want regression through the origin, not through the means of the data.)
```{r}
lre <- lm(y ~ x - 1)
coef(lre)
```
#Question 3
Do data(mtcars) from the datasets package and fit the regression model with mpg as the outcome and weight as the predictor. Give the slope coefficient.
```{r}
data(mtcars)
lre <- lm(mpg ~ wt, data = mtcars)
summary(lre)
coef(lre)["wt"]
```
#Question 6
Consider the data given by the following
```{r}
x <- c(8.58, 10.46, 9.01, 9.64, 8.86)
```
What is the value of the first measurement if x were normalized (to have mean 0 and variance 1)?
```{r}
x_norm <- (x-mean(x))/sd(x)
x_norm[[1]]
```
#Question 7
Consider the following data set (used above as well). What is the intercept for fitting the model with x as the predictor and y as the outcome?
```{r}
x <- c(0.8, 0.47, 0.51, 0.73, 0.36, 0.58, 0.57, 0.85, 0.44, 0.42)
y <- c(1.39, 0.72, 1.55, 0.48, 1.19, -1.59, 1.23, -0.65, 1.49, 0.05)

lre <- lm(y ~ x)
coef(lre)[1]
```
#Question 9
Consider the data given by
```{r}
x <- c(0.8, 0.47, 0.51, 0.73, 0.36, 0.58, 0.57, 0.85, 0.44, 0.42)
```
What value minimizes the sum of the squared distances between these points and itself?
```{r}
mean(x)
```



